COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-04-15 main.tex
Add figure captions, add new figure showing change in collision rate with ejup and mjup

%Things to change/do:
%    Transient feature in EJ collision rate before 2000 years. Only want to look at collisions after this time. Mention this when discussing figure 4. Justify the cutoff (maybe something to do with precession in 3:1 MMR?)
%    Safronov and Nbody collision rates. Not matching up well near resonance. The 'wings' from the resonances mess up calculation of velocity dispersion. Maybe do comparison
%       no grav focusing?
%    Get Aaron to make some dust emission makes from the Nbody collision histograms
%    Can we scale these results to any size system? Get rid of units. How to justify planetesimal size?

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/xy.png}
    \caption{Caption goes here.\label{fig:xy}}
\end{figure*}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.4\columnwidth]{figures/ae.png}
    \caption{Caption goes here.\label{fig:ae}}
    \end{center}
\end{figure}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.4\columnwidth]{figures/long_ph.png}
    \caption{Caption goes here.\label{fig:long_ph}}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.4\columnwidth]{figures/coll_hist_a.png}
    \caption{Caption goes here.\label{fig:coll_hist_a}}
    \end{center}
\end{figure}

@@

@@

Finally, the bottom row of figure \ref{fig:coll_hist_r} demonstrates the difficulty with calculating the collision rate from the position and velocity 
distribution of particles. At a given distance from the central star, the distribution of velocities (using eccentricity as a proxy for typical encounter 
velocity), is not unimodal. In addition, the wings extending off of the resonances in these plots show that planetesimals can interact and collide 
with bodies far from the centers of the resonances. The bump seen in the collision rate in the EJ simulation around 2.7 AU is like a result of the 
complicated interaction between planetesimals in the 3:1, 5:2 and 2:1 resonances.

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/coll_hist_r.png}
    \caption{Caption goes here.\label{fig:coll_hist_r}}
\end{figure*}

@@

>>>>

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/xy.png}
    \caption{The positions of remaining planetesimals at the end of the CJ (left) and EJ (right) simulations. Jupiter's position is
    indicated by a red dot. Nonaxisymmetric features due to mean motion resonances are clearly visible in both cases. Higher
    order resonances are visible in the EJ case.\label{fig:xy}}
\end{figure*}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.4\columnwidth]{figures/ae.png}
    \caption{The semimajor axis - eccentricity state of the remaining planetesimals are shown at the end of the CJ (top) and EJ (bottom) 
    simulations. The vertical bars mark the nominal locations of prominent resonances. Planetesimals affected by resonance with Jupiter gain
     eccentricity, and due to conservation of the Jacobi energy, reduce their semimajor axes. This produces the curved fingerlike structure 
     extending off of the resonances. In the EJ case, some bodies in resonance take on eccentricities smaller than their initial forced values as 
     they undergo libration.\label{fig:ae}}
    \end{center}
\end{figure}

@@

\begin{figure}
    \begin{center}
    \includegraphics[width=0.4\columnwidth]{figures/long_ph.png}
    \caption{The semimajor axis and pericenter orientation of remaining planetesimals at the end of the EJ simulation. All bodies start with their 
    pericenters closely aligned with Jupiter's ($\varpi = \pi$). Near the resonances, bodies undergo strong precession which randomizes their 
    orbital orientations. Two-body interactions between the planetesimals in resonance and nearby non-resonant planetesimals drags their 
    longitude of perihelia along with.\label{fig:long_ph}}
    \end{center}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.4\columnwidth]{figures/coll_hist_a.png}
    \caption{A kernel density estimate (KDE) of the collision rate as a function of semimajor axis in the CJ (top) and EJ (bottom) simulations. 
    There are measureable changes in the collision rate near 2:1 and 3:1 MMRs, each of which produce qualitatively different changes in the 
    collision rate. The vertical bars mark the nominal locations of prominent resonances.\label{fig:coll_hist_a}}
    \end{center}
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{figures/coll_hist_r.png}
    \caption{\textit{Top:} A KDE of the collision rate in the CJ (left) and EJ (right) simulations as a function of cylindrical distance from the central 
    star. Vertical lines mark the nominal locations of the MMRs. Variations in the collision rate are visible near the MMRs, but are distinctly 
    different than the feature that appeared in figure \ref{fig:coll_hist_a}. \textit{Middle:} The azimuthally-averaged surface density of remaining 
    planetesimals. \textit{Bottom:} The cylindrical distance and eccentricities of remaining planetesimals. The cones extending upward from the 
    resonance locations are due to the fact that eccentric planetesimals explore a wide range of physical space over the course of an orbit.\label{fig:coll_hist_r}}
\end{figure*}

@@

Finally, the bottom row of figure \ref{fig:coll_hist_r} demonstrates the difficulty with calculating the collision rate from the position and velocity 
distribution of particles. At a given distance from the central star, the distribution of velocities (using eccentricity as a proxy for encounter 
velocity), is not unimodal. In addition, the wings extending off of the resonances in these plots show that planetesimals can interact and collide 
with bodies far from the centers of the resonances. The bump seen in the collision rate in the EJ simulation around 2.7 AU is like a result of interaction between planetesimals in the 3:1, 5:2 and 2:1 resonances.

@@

@@

\begin{figure*}
    \includegraphics[width=0.4\textwidth]{figures/coll_hist_e_and_m.png}
    \caption{Caption goes here.\label{fig:coll_hist_e_and_m}}
\end{figure*}
